Acceleration of plague outbreaks in the second pandemic

### 2020-07-03 ms_text.tex
additional keywords
amsync

\leftline{plague $|$ London $|$ epidemic growth rate}

@@

The city of London, England, is unusual in the extent to which patterns of death and disease can be reconstructed from extant documents. We have analyzed three sources of data (\cref{F:plot3sources}):
\begin{description}
\item[London Bills of Mortality] The London Bills of Mortality \cite{Crei65,Tien+11} (LBoM) provide weekly counts of deaths by cause during each of the known plague epidemics in the 16th and 17th centuries.  The LBoM thus give us information specifically about mortality attributable to plague for each epidemic, which we will use as a proxy for plague incidence \cite{KermMcKe27,Ma+14}.  When available, the LBoM are our most reliable records (except for the epidemic of 1593; see \supp).
\item[Parish registers] After 1538 \cite[p.\,54]{Slac90}, London parish registers provide information on mortality.
%%, although these are not categorized by cause. 
We use weekly counts of deaths published online by Cummins, which are estimated to cover 80\% of total deaths \cite{Cumm+16}. During plague epidemics, most deaths were likely due to plague; we also adjust for non-plague mortality by estimating a baseline death rate from the years before and after an epidemic (see \Methodslink).
\hypertarget{mainsec:Data.wills}{}
\item[Wills and testaments] Before 1538, no direct tabulations of mortality for London are available. However, we do have detailed information on last wills and testaments, which can be used as proxies for mortality \cite{Slac90}. In particular, we have digitized and tabulated daily counts of wills recorded in the Court of Husting \cite{Shar1889} for the 14th century; these give us data for the plague epidemics of 1348, 1361, 1368 and 1375 (monthly counts for three of these epidemics were previously published by Cohn \cite{Cohn03}). We use online data from the Prerogative Court of Canterbury (PCC) \cite{Archives2018} 
for the plague epidemics of the 16th and 17th century.  Plague epidemics in London are mentioned in historical documents from the 15th century \cite[Ch.\,IV]{Crei65}, but during this period wills recorded in the Courts of Husting and Canterbury were too sparse to enable identification of epidemics.

>>>>

\leftline{plague $|$ London $|$ epidemic growth rate $|$ reproduction number $|$ SARS-CoV-2 $|$ COVID-19}

@@

The city of London, England, is unusual in the extent to which patterns of death and disease can be reconstructed from extant documents. We have analyzed three sources of data (\cref{F:plot3sources}):
\begin{description}
\item[London Bills of Mortality] The London Bills of Mortality \cite{Crei65,Tien+11} (LBoM) provide weekly counts of deaths by cause during each of the known plague epidemics in the 16th and 17th centuries.  The LBoM thus give us information specifically about mortality attributable to plague for each epidemic, which we will use as a proxy for plague incidence \cite{KermMcKe27,Ma+14}.  When available, the LBoM are our most reliable records (except for the epidemic of 1593; see \supp).
\item[Parish registers] After 1538 \cite[p.\,54]{Slac90}\cite{Wall04}, London parish registers provide information on mortality.
%%, although these are not categorized by cause. 
We use weekly counts of deaths published online by Cummins, which are estimated to cover 80\% of total deaths \cite{Cumm+16}. During plague epidemics, most deaths were likely due to plague; we also adjust for non-plague mortality by estimating a baseline death rate from the years before and after an epidemic (see \Methodslink).
\hypertarget{mainsec:Data.wills}{}
\item[Wills and testaments] Before 1538, no direct tabulations of mortality for London are available. However, we do have detailed information on last wills and testaments, which can be used as proxies for mortality \cite{Slac90}. In particular, we have digitized and tabulated daily counts of wills recorded in the Court of Husting \cite{Shar1889} for the 14th century; these give us data for the plague epidemics of 1348, 1361, 1368 and 1375 (monthly counts for three of these epidemics were previously published by Cohn \cite{Cohn03}). We use online data from the Prerogative Court of Canterbury (PCC) \cite{Archives2018} 
for the plague epidemics of the 16th and 17th century.  Plague epidemics in London are mentioned in historical documents from the 15th century \cite[Ch.\,IV]{Crei65}, but during this period wills recorded in the Courts of Husting and Canterbury were too sparse to enable identification of epidemics.
